---
title: "Employee Job Satisfaction Survey Analysis"
author: "Group 1"
output: html_document
runtime: shiny
---

## Introduction

The survey we designed was about the empoyees' job satisfaction rating in ABS company. The nubmer 1 to 5 quesitons were about the satisfaction rating about income&benefits, relationship, resource, learning&growthing oppotunities and work/life balance. The number 6 question asked about the over all job satisfaction level. We plan to use the answer of the number 6 question as our goal (dependent variable) and try to find out how the answers of quistion 1-5 may impact the overall job satisfaction level of empolyees.

Survey Form:

https://goo.gl/forms/ktTaOUXBTaqDYVQz1

Survey Data:

https://docs.google.com/spreadsheets/d/1ird97kCnDg2YT7VAAp78LfSJICuArNLTvYEJd70Ajk8/edit?usp=sharing

```{r setup, include=FALSE}
# load packages
library(tidyverse)
library(magrittr)
library(DT)
library(readr)
survey_result <- readr::read_rds("survey_result.rds")
```

## Bar charts

Show the distribution of different responses result.

```{r, echo = FALSE}
selectInput(inputId = 'var', 
            label = 'Select a Variable', 
            choices = names(survey_result),
            selected = names(survey_result)[[1]]
            )
```

```{r, echo = FALSE}
renderPlot({
    survey_result %>% 
    ggplot(aes(x = survey_result[[input$var]])) +
    geom_bar(stat = "count", width = 0.7) +
    labs(x = input$var)
})
```

## Mosaic chart

```{r, echo = FALSE}
survey_result_long <- survey_result %>% 
  gather(key = name, value = satisfication)

survey_result_long %>% 
  ggplot(aes(x = name, fill = satisfication)) +
  geom_bar(position = "fill") + 
  coord_flip()
```

#### Analysis

  - `salary and benefits` seems more related with the `overall satisfication`
  - `resources` and `relation with manager` seems to have the highest ratings, which means the company provides enough resources to employees to perform their jobs.

## Correlation table

```{r, echo = FALSE}
cor_table <- survey_result %>% 
  na.omit() %>% 
  map_dfc(as.double) %>% 
  stats::cor() 

cor_table[] %<>% 
  map_dbl(round, digits = 3)

DT::datatable(cor_table)
```

#### Analysis:

  - `salary and benefits` are the highly correlated with the `overall satisfication` as compared with other variables.
  - `Learning and growth opportunities` also affect employee's `overall satisfication`.
  - However, work life balance is not highly correlated with `overall satisfication`, this means that the company can improve the `work life balance` of employees
  

## Linear Regression

```{r}
formula <- overall ~ salary_and_benefits + relation_with_manager + resources + opportunties + work_life_balance

lm_fit <- lm(formula = formula, data = survey_result %>% map_dfc(as.double))

summary(lm_fit)
```

#### Analysis

  - `salary and benefits` and `resources` are significant
  - R-square is high
  - dataset is probably a little small